Visualize Non-Euclidean Actors Social Media via Joint Social Relationship Representations, Network Characteristics and Media Sentiments

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr.tex
1.follow CVPR call for paper, remove arXiv references.

Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table 1.
$Power-LawBound_{a-f}$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Algorithm	& Time Cost \\
\hline\hline
Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem}  &	1055880s \\
Alon \etal          &	594.7s \\
$Power-LawBound_a$ 	&	427.9s \\
$Power-LawBound_b$	&	328.4s \\
$Power-LawBound_c$	&	95.0s \\
$Power-LawBound_d$	&	45.0s \\
$Power-LawBound_e$	&	19.32s \\
$Power-LawBound_f$	&	15.98s \\
\hline
\end{tabular}
\end{center}
\caption{Performance comparison on different hardware. (a) CPU numpy library. (b) CPU scipy/numpy library. (c) GPU cuBLAS. (d) CPU openBLAS. (e) GPU CuPy. (f) GPU CuPy-sparse/CuPy.}
\end{table}

>>>>

Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table 1.
$Power-LawBound(a-f)$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Algorithm	& Time Cost \\
\hline\hline
Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem}  &	1055880s \\
Alon \etal~\cite{alon1997exponent}  &	594.7s \\
$Power-LawBound(a)$ &	427.9s \\
$Power-LawBound(b)$	&	328.4s \\
$Power-LawBound(c)$	&	95.0s \\
$Power-LawBound(d)$	&	45.0s \\
$Power-LawBound(e)$	&	19.32s \\
$Power-LawBound(f)$	&	15.98s \\
\hline
\end{tabular}
\end{center}
\caption{Performance comparison on different hardware. (a) CPU numpy library. (b) CPU scipy/numpy library. (c) GPU cuBLAS. (d) CPU openBLAS. (e) GPU CuPy. (f) GPU CuPy-sparse/CuPy.}
\end{table}

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.follow CVPR call for paper, remove arXiv references.

  Unsupervised pre-training is important in modern research of deep learning.
  Lee \etal~\cite{lee2009convolutional} used pre-training approaches
  in Computer Vision tasks in 2009, and later from 2010 to 2016, Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the CV tasks,
  thus, can be omitted in some cases.
  However, it started to flourish in natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
  Not long before Devin \etal~\cite{devlin2018bert}'s BERT language model dominates in most frequent used tasks in natural language processing,
  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
  Pre-training process become one of the most important procedures in deep learning.

@@

  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show its outperforming to Wide-ResNet
which inspired from unsupervised natural language representation learning.
  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in 1960s, and had its implementation in 1980s,
and until LeCun \etal~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
  In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
Wide-ResNet~\cite{zagoruyko2016wide}, ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
  Lu and Weng~\cite{lu2007survey} concluded that for multi-source image classification task, additional information such as signatures, texture, context and ancillary data can be combined to achieve better performance.
And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
  Cui \etal~\cite{cui2019pre, cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
which are improved versions of BERT~\cite{devlin2018bert} and RoBERTa~\cite{liu2019roberta} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
These models achieved better performance in Chinese machine reading comprehension, Chinese document classification and other downstream natural language tasks.
  He and Peng~\cite{he2017fine} combined vision stream and language stream as two parallel channels for extracting multi-source information in the imaege classification,
and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.

@@

\par Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
\eg support vector machines and conditional random field, in many dataset such as, movie reviews, Stanford sentiment treebank, and TREC question.
Adhikari \etal~\cite{adhikari2019docbert} showed the BERT and BERT-large model had achieved higher accuracy in the Routers, IMDB, and Yelp dataset which classification ranges from 5 to 90.
Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
BERT and RoBERTa-wwm-ext-large models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands of news in 10 domains.

@@

As Cui \etal~\cite{cui2019pre} reported that the training of RBT3 language model was based on Devlin \etal's
Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
I use a batch size of 512 and train for $1\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
I set the learning rate to $10^{-4}$ and no warmed up or decay are used.
The dropout rate is $0.05$.

>>>>

  Unsupervised pre-training is important in modern research of deep learning.
  Lee \etal~\cite{lee2009convolutional} used pre-training approaches
  in Computer Vision tasks in 2009, and later from 2010 to 2016, Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the CV tasks,
  thus, can be omitted in some cases.
  However, it started to flourish in natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
  Not long before Devin \etal~\cite{devlin2019bert}'s BERT language model dominates in most frequent used tasks in natural language processing,
  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
  Pre-training process become one of the most important procedures in deep learning.

@@

  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show its outperforming to Wide-ResNet
which inspired from unsupervised natural language representation learning.
  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in 1960s, and had its implementation in 1980s,
and until LeCun \etal~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
  In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
 ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
  Lu and Weng~\cite{lu2007survey} concluded that for multi-source image classification task, additional information such as signatures, texture, context and ancillary data can be combined to achieve better performance.
And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
  Cui \etal~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
These models achieved better performance in Chinese machine reading comprehension, Chinese document classification and other downstream natural language tasks.
  He and Peng~\cite{he2017fine} combined vision stream and language stream as two parallel channels for extracting multi-source information in the imaege classification task,
and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.

@@

\par Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
\eg support vector machines and conditional random field, in many dataset such as, movie reviews, Stanford sentiment treebank, and TREC question.
Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
BERT and RoBERTa-wwm-ext-large models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands of news in 10 domains.

@@

As Cui \etal~\cite{cui2020revisiting} reported that the training of RBT3 language model was based on Devlin \etal's
Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
I use a batch size of 512 and train for $1\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
I set the learning rate to $10^{-4}$ and no warmed up or decay are used.
The dropout rate is $0.05$.

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.follow CVPR call for paper, remove arXiv references.

  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential to movie producers.
  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, also named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
  On the analysis of social media , social relationship representations, network characteristics and media sentiments are key factors.
  FC-GRU-CNN architecture exploits the long-term memory ability of GRU layer in long sequences of film cast,
  the mapping ability of CNN layer in retrieving all-pairs shortest path feature of the actors' social relationship,
  and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
  The proposed model accuracy is 14\% higher than Zhou \etal's model.

@@

  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spreads through social networks,
  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to get the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film meta-data, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artisticcontribution characteristics,
  as a result, it is 14\% higher in accuracy than Zhou \etal ~\cite{zhou2015c}'s model.

@@

  Zhou \etal~\cite{zhou2015c} proposed a C-LSTM classification model, using single-layer CNN for extracting the high-order dimensional representation of text,
  and connecting to LSTM layers for sentence representation, the trained neural network model has an accuracy of 87.8\%.

>>>>

  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential to movie producers.
  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, also named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
  On the analysis of social media , social relationship representations, network characteristics and media sentiments are key factors.
  FC-GRU-CNN architecture exploits the long-term memory ability of GRU layer in long sequences of film cast,
  the mapping ability of CNN layer in retrieving all-pairs shortest path feature of the actors' social relationship,
  and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
  The proposed model accuracy is 14\% higher than Shi \etal's model.

@@

  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spreads through social networks,
  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to get the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film meta-data, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artisticcontribution characteristics,
  as a result, it is 14\% higher in accuracy than Shi \etal ~\cite{shi2019c}'s model.

@@

  Shi \etal~\cite{shi2019c} proposed a C-LSTM classification model, using single-layer CNN for extracting the high-order dimensional representation of text,
  and connecting to LSTM layers for sentence representation, the trained neural network model has an accuracy of 87.8\%.
